Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-10-04 forgerard.tex
version for collaboration resubmission

\title{Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory}
\author{A.~G.~Kim}
\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
    1 Cyclotron Road, Berkeley, CA, 94720}

@@

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be 
dependent on the spectral equivalent widths and two independent color parameters, with better than 
%-----
 $98$\%
%------
confidence.
One parameter, interpreted as due to extrinsic host-galaxy
dust extinction, is consistent with a \citet{1999PASP..111...63F} dust model with
%-----
$R_V=2.97^{+0.18}_{-0.17}$.
%------
 The second parameter is inconsistent with dust and
is inferred to have origins intrinsic to supernovae.  Our model explains features of external data: 
\textcolor{red}{
indirect evidence for intrinsic color dispersion from Hubble residuals;
the wide range of inferred $R_V$ among
SNe~Ia; the systematically lower inferred $R_V$ of redder supernovae;}
and the colors of SN~2014J,.
\textcolor{red}{
The new parameter
provides a handle with which to interpret  Hubble-residual correlations with host-galaxy properties,}
\end{abstract}

@@

Supernova-frame synthetic photometry is generated for a top-hat filter system
comprised of five 
\color{red}
bands with the following wavelength ranges: $U$ $[3300.00 - 3978.02]$\AA;
$B$ $[3978.02-4795.35]$\AA;
$V$ $[4795.35-5780.60]$\AA;
$R$ $[5780.60-6968.29]$\AA;
$I$ $[6968.29-8400.00]$\AA.
\color{black}
For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
in \citet{2008A&A...477..717B} and the 
\textcolor{red}{wavelength of the SiII$\lambda 6355$ feature}
as in \citet{chotard:thesis}.
Equivalent widths and the
\textcolor{red}{SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from maximum, in the case of multiple spectra the one
closest to maximum is used \citep{chotard:thesis}. [Confirm!]
The weighted mean is used for the  SiII$\lambda 6355$ wavelength.}

@@

We hypothesize that at peak brightness
SN~Ia broadband magnitudes and colors are correlated with
spectral features: equivalent widths and line positions are considered as statistics localized in wavelength that are insensitive to variations in
broadband colors.
%Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
%of intrinsic variation is accommodated.
The intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
\textcolor{red}{The intrinsic magnitudes are then
modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.}
\subsection{Model}
We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the
 equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
\textcolor{red}{ and $\lambda_{Si}$ the wavelength of the minimum of 
the SiII$\lambda6355$ feature}:
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
\textcolor{red}{
The explicit omission of light-curve shape in our model is compensated by its proxy
$EW_{Si}$ at peak brightness}
\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
% An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on the
extrinsic-color parameters $k_0$ and $k_1$.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
The model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si}  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si}
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$,  and $\eta$,  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters.
(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
parameter and observed magnitudes.

To constrain the degrees of freedom and degeneracies inherent in the model we impose that
\color{red}
each of the vectors $k_0+1/N$ and $k_1+1/N$ are simplexes, where $N$ is the number of objects in our sample: these
conditions break the 
degeneracies  $\gamma ^0\rightarrow a\gamma^0$, $k_0 \rightarrow a^{-1}k_0$ and $\gamma^1 \rightarrow a\gamma^1$, $k_1 \rightarrow a^{-1}k_1$.
Furthermore we impose
\color{black} 
\begin{equation}
\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \gamma^0_0 > 0, \gamma^1_0 < 0.
\end{equation}
The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
associated
with  simultaneous sign flips of
$\gamma^0$--$k_0$ and $\gamma^1$--$k_1$
\color{red}
(when running our fits, $k_0$ and $k_1$ are set to
identical initial conditions, so the difference in the signs of $\gamma^0_0$ and $\gamma^1_0$ distinguishes the two.)
As  $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
each other,
the different initial and boundary conditions for $\gamma^0_0$ and $\gamma^1_0$ break the degeneracy of our mixture model;
otherwise identical initial conditions for $\gamma^0$, $\gamma^1$ produce indistinguishable posteriors
with relatively broad credible intervals and lower maximum likelihood.

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0043^{0.0009}_{-0.0009}$
&
$0.0016^{0.0007}_{-0.0007}$
&
$0.0015^{0.0006}_{-0.0006}$
&
$0.0015^{0.0005}_{-0.0005}$
&
$0.0026^{0.0005}_{-0.0004}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.9^{   1.0}_{  -0.5}$
&
$   0.1^{   0.1}_{  -0.2}$
&
$   0$
&
$  -0.0^{   0.1}_{  -0.1}$
&
$   0.7^{   0.7}_{  -0.3}$
\\
$\beta_X$
&
$ 0.032^{ 0.003}_{-0.003}$
&
$ 0.025^{ 0.002}_{-0.003}$
&
$ 0.025^{ 0.002}_{-0.002}$
&
$ 0.020^{ 0.002}_{-0.002}$
&
$ 0.019^{ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.26^{  0.05}_{ -0.05}$
&
$ -0.01^{  0.03}_{ -0.03}$
&
$  0$
&
$ -0.19^{  0.01}_{ -0.01}$
&
$ -0.24^{  0.03}_{ -0.03}$
\\
$\eta_X$
&
$-0.0002^{0.0012}_{-0.0011}$
&
$-0.0000^{0.0010}_{-0.0009}$
&
$0.0005^{0.0008}_{-0.0008}$
&
$0.0005^{0.0007}_{-0.0007}$
&
$-0.0003^{0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.40^{  2.33}_{ -1.90}$
&
$ -0.34^{  1.60}_{ -1.20}$
&
$  0$
&
$ -0.11^{  0.29}_{ -0.27}$
&
$ -0.84^{  1.66}_{ -1.27}$
\\
$\gamma^0_X$
&
$ 62.16^{  3.68}_{ -3.52}$
&
$ 50.39^{  3.05}_{ -2.96}$
&
$ 37.38^{  2.58}_{ -2.52}$
&
$ 28.71^{  2.31}_{ -2.25}$
&
$ 20.61^{  2.15}_{ -2.11}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.66^{  0.06}_{ -0.05}$
&
$  0.35^{  0.03}_{ -0.03}$
&
$  0$
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$ -9.75^{  3.39}_{ -4.14}$
&
$-11.82^{  2.78}_{ -3.35}$
&
$-14.26^{  2.38}_{ -2.73}$
&
$-13.35^{  2.09}_{ -2.30}$
&
$-11.91^{  2.01}_{ -2.15}$
\\
${\gamma^1_X/\gamma^1_2-1}$
&
$ -0.31^{  0.17}_{ -0.18}$
&
$ -0.17^{  0.09}_{ -0.10}$
&
$  0$
&
$ -0.07^{  0.05}_{ -0.04}$
&
$ -0.17^{  0.10}_{ -0.09}$
\\
$\sigma_X$
&
$ 0.060^{ 0.012}_{-0.012}$
&
$ 0.033^{ 0.007}_{-0.007}$
&
$ 0.021^{ 0.004}_{-0.006}$
&
$ 0.012^{ 0.007}_{-0.008}$
&
$ 0.044^{ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible Intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model \label{global:tab}}
\end{table}

@@

\subsection{Two Extrinsic Parameters $k_0$ and $k_1$}
\color{red}
The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
\color{black}
None of the 20000 links of 
our Monte Carlo chains for $\gamma$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
influence of $k_0$ and $k_1$  on supernova magnitudes
with probability $(1-5\times 10^{-5})$.

\color{red}
Combining the effects of both parameters, we can define a total $X$-band extinction $A_X=\gamma^0_X k_0 + \gamma^1_X k_1$
and a corresponding $E(B-V) = A_B-A_V$.  Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
which a linear fit gives a slope of $R_V=2.51^{+0.23}_{-0.21}$.  The fit also gives the zeropoint, which we use to 
estimate $R_V=A_V/(E(B-V)-zeropoint)$ per supernova, shown in Figure~\ref{avebv:fig}.
Extremely blue supernovae ($E(B-V) + const <-0.05$ on the plot) have an average $R_V=1.88 \pm   0.13$,
whereas the extreme red objects ($E(B-V) + const >0.1$) have $R_V=  2.52 \pm   0.08$, indicating that different physics
operate in these regimes.

@@

For the linear 2-parameter model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
It turns out that the planes for both our and the Fitzpatrick dust model are nearly parallel, in that
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
\end{pmatrix}=
\begin{pmatrix}
1.15 & 2.82 \\
0.75 & -5.43
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\vec{\epsilon},
\end{equation}
where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
contribute  2\% and 5\% to the total  length of the vector.

The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
are projected onto the Fitzpatrick values of $E^F(B-V)$ and $A^F$, up to a constant:  these are shown in Figure~\ref{avebv:fig}.
The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.43^{+0.16}_{-0.17}$.  
The linear fit also produces the zeropoint, allowing us to determine $R^F_V$ for each supernova,
which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
the native $R_V$, $A_V$, and $E(B-V)$  shown in Figure~\ref{avebv:fig}.

@@

The near coplanarity of the plane defined by our parameters and the plane of Fitzpatrick, together with the fact that our the individual supernova
parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$ lead us to conclude that 
external dust is responsible for most of our $k_0$ and $k_1$ parameters.

@@

Data of SN~2014J are  analyzed using our model and the parameter values found with the SNfactory sample.
The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
following their perscription of averaging measurements within 5-days of peak $B$ magnitude.
Their values 
$E_o(U-V) =   2.23 \pm   0.03$,
$E_o(B-V) =   1.28 \pm   0.04$,
$E_o(R-V) =  -0.47 \pm   0.03$,
$E_o(i-V) =  -0.92 \pm   0.03$
are plotted in Figure~\ref{sn2014j:fig}.
These data are fit to the model
\begin{equation}
E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)k_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)k_1,
\end{equation}
where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab}.

@@

The best-fit parameters for SN~2014J are 
%----
$k_0= 2.65$, $ k_1=-1.64$ with covariance
%----
\begin{equation}
\begin{pmatrix}
0.048 & 0.047 \\
0.047 & 0.248
\end{pmatrix}.
\end{equation}
The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} using
UV through NIR data,
a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$, 
is also plotted.  Our model predictions provide a significantly better match to the data.

>>>>

\title{Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory}
\author{A.~G.~Kim}
\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
    1 Cyclotron Road, Berkeley, CA, 94720}

@@

\begin{abstract}
\color{red}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the spectral equivalent widths and two independent color parameters, to better than 
%-----
$(1-5\times10^{-5})$
%------
confidence.
The two parameters exhibit the behavior expected from the two-parameter
\citet{1999PASP..111...63F} dust model with a per-supernova scatter in
total-to-selective extinction, an effective
%-----
$R^F_V=2.43^{+0.16}_{-0.17}$
%------
for the full sample, and a difference in the average $R^F_V$ between extremely blue and red supernovae .  The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J.
Extending the model to allow three color parameters gives a detection of a third parameter at  $>98$\% confidence.
\color{black}
\end{abstract}

@@

Supernova-frame synthetic photometry is generated for a top-hat filter system
comprised of five 
\color{red}
bands with the following wavelength ranges: $U$ $[3300.00 - 3978.02]$\AA;
$B$ $[3978.02-4795.35]$\AA;
$V$ $[4795.35-5780.60]$\AA;
$R$ $[5780.60-6968.29]$\AA;
$I$ $[6968.29-8400.00]$\AA.
\color{black}
For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
in \citet{2008A&A...477..717B} and the 
\textcolor{red}{wavelength of the SiII$\lambda 6355$ feature}
as in \citet{chotard:thesis}.
Equivalent widths and the
\textcolor{red}{SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from maximum, in the case of multiple spectra the one
closest to maximum is used \citep{chotard:thesis}.
The weighted mean is used for the  SiII$\lambda 6355$ wavelength.}

@@

We hypothesize that at peak brightness
SN~Ia broadband magnitudes and colors are correlated with
spectral features: equivalent widths and line positions are considered as statistics localized in wavelength that are insensitive to variations in
broadband colors.
%Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
%of intrinsic variation is accommodated.
The intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
\textcolor{red}{The intrinsic magnitudes are then
modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.}
\subsection{Model}
We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the
 equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
\textcolor{red}{ and $\lambda_{Si}$ the wavelength of the minimum of 
the SiII$\lambda6355$ feature}:
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
\textcolor{red}{
The explicit omission of light-curve shape in our model is compensated by its proxy
$EW_{Si}$ at peak brightness}
\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
% An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on the
extrinsic-color parameters $k_0$ and $k_1$.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
The model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si}  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si}
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$,  and $\eta$,  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters.
(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
parameters to observed magnitudes.

To constrain the degrees of freedom and degeneracies inherent in the model we impose that
\color{red}
each of the vectors $k_0+1/N$ and $k_1+1/N$ are simplexes, where $N$ is the number of objects in our sample: these
conditions break the 
degeneracies  $\gamma ^0\rightarrow a\gamma^0$, $k_0 \rightarrow a^{-1}k_0$ and $\gamma^1 \rightarrow a\gamma^1$, $k_1 \rightarrow a^{-1}k_1$
up to the $\pm$ sign.
Furthermore we impose
\color{black} 
\begin{equation}
\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \gamma^0_0 > 0, \gamma^1_0 < 0.
\end{equation}
The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
associated
with  simultaneous sign flips of
$\gamma^0$--$k_0$ and $\gamma^1$--$k_1$
\color{red}
(when running our fits, $k_0$ and $k_1$ are set to
identical initial conditions, so the difference in the signs of $\gamma^0_0$ and $\gamma^1_0$ distinguishes the two.)
As  $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
each other,
the different initial and boundary conditions for $\gamma^0_0$ and $\gamma^1_0$ break the degeneracy of our mixture model;
otherwise identical initial conditions for $\gamma^0$, $\gamma^1$ produce indistinguishable posteriors
with relatively broad credible intervals and lower maximum likelihood.

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0043^{0.0009}_{-0.0009}$
&
$0.0016^{0.0007}_{-0.0007}$
&
$0.0015^{0.0006}_{-0.0006}$
&
$0.0015^{0.0005}_{-0.0005}$
&
$0.0026^{0.0005}_{-0.0004}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.9^{   1.0}_{  -0.5}$
&
$   0.1^{   0.1}_{  -0.2}$
&
$   0$
&
$  -0.0^{   0.1}_{  -0.1}$
&
$   0.7^{   0.7}_{  -0.3}$
\\
$\beta_X$
&
$ 0.032^{ 0.003}_{-0.003}$
&
$ 0.025^{ 0.002}_{-0.003}$
&
$ 0.025^{ 0.002}_{-0.002}$
&
$ 0.020^{ 0.002}_{-0.002}$
&
$ 0.019^{ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.26^{  0.05}_{ -0.05}$
&
$ -0.01^{  0.03}_{ -0.03}$
&
$  0$
&
$ -0.19^{  0.01}_{ -0.01}$
&
$ -0.24^{  0.03}_{ -0.03}$
\\
$\eta_X$
&
$-0.0002^{0.0012}_{-0.0011}$
&
$-0.0000^{0.0010}_{-0.0009}$
&
$0.0005^{0.0008}_{-0.0008}$
&
$0.0005^{0.0007}_{-0.0007}$
&
$-0.0003^{0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.40^{  2.33}_{ -1.90}$
&
$ -0.34^{  1.60}_{ -1.20}$
&
$  0$
&
$ -0.11^{  0.29}_{ -0.27}$
&
$ -0.84^{  1.66}_{ -1.27}$
\\
$\gamma^0_X$
&
$ 62.16^{  3.68}_{ -3.52}$
&
$ 50.39^{  3.05}_{ -2.96}$
&
$ 37.38^{  2.58}_{ -2.52}$
&
$ 28.71^{  2.31}_{ -2.25}$
&
$ 20.61^{  2.15}_{ -2.11}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.66^{  0.06}_{ -0.05}$
&
$  0.35^{  0.03}_{ -0.03}$
&
$  0$
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$ -9.75^{  3.39}_{ -4.14}$
&
$-11.82^{  2.78}_{ -3.35}$
&
$-14.26^{  2.38}_{ -2.73}$
&
$-13.35^{  2.09}_{ -2.30}$
&
$-11.91^{  2.01}_{ -2.15}$
\\
${\gamma^1_X/\gamma^1_V-1}$
&
$ -0.31^{  0.17}_{ -0.18}$
&
$ -0.17^{  0.09}_{ -0.10}$
&
$  0$
&
$ -0.07^{  0.05}_{ -0.04}$
&
$ -0.17^{  0.10}_{ -0.09}$
\\
$\sigma_X$
&
$ 0.060^{ 0.012}_{-0.012}$
&
$ 0.033^{ 0.007}_{-0.007}$
&
$ 0.021^{ 0.004}_{-0.006}$
&
$ 0.012^{ 0.007}_{-0.008}$
&
$ 0.044^{ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model \label{global:tab}}
\end{table}

@@

\subsection{The Two Extrinsic Parameters $k_0$ and $k_1$}
\color{red}
The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
\color{black}
None of the 20000 links of 
our Monte Carlo chains for $\gamma$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
influence of $k_0$ and $k_1$  on supernova magnitudes
with probability $(1-5\times 10^{-5})$.

\color{red}
Combining the effects of both parameters, we can define a total $X$-band extinction $A_X=\gamma^0_X k_0 + \gamma^1_X k_1$
and a corresponding $E(B-V) = A_B-A_V$.  Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
which a linear fit gives a slope of $R_V=2.51^{+0.23}_{-0.21}$.  The fit also gives the zeropoint, which we use to 
estimate $R_V=(A_V-zeropoint)/E(B-V)$ per supernova, shown in Figure~\ref{avebv:fig}.
Extremely blue supernovae ($E(B-V) + const <-0.05$ on the plot) have an average $R_V=1.88 \pm   0.13$,
whereas the extreme red objects ($E(B-V) + const >0.1$) have $R_V=  2.52 \pm   0.08$, indicating that different physics
operate in these regimes.

@@

For a linear 2-parameter model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
It turns out that the planes for both our and the Fitzpatrick dust model are nearly parallel, in that
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
\end{pmatrix}=
\begin{pmatrix}
1.15 & 2.82 \\
0.75 & -5.43
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\vec{\epsilon},
\end{equation}
where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
contribute  2\% and 5\% to the total  length of the vector.

The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
are projected onto the Fitzpatrick values of $E^F(B-V)$ and $A^F$, up to an additive constant:  these are shown in Figure~\ref{avebv:fig}.
The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.43^{+0.16}_{-0.17}$.  
The linear fit also produces the zeropoint, allowing us to determine individual $R^F_V$ for all supernovae,
which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
the native $R_V$, $A_V$, and $E(B-V)$  shown in Figure~\ref{avebv:fig}.

@@

The near coplanarity of the plane defined by our parameters and the plane of Fitzpatrick, together with the fact that our the individual supernova
parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$, lead us to conclude that 
$k_0$, $k_1$, $\gamma^0$, $\gamma^1$ describe for the most part
external dust.

@@

Data of SN~2014J are  analyzed using our model and the parameter values found with the SNfactory sample.
The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
Their values 
$E_o(U-V) =   2.23 \pm   0.03$,
$E_o(B-V) =   1.28 \pm   0.04$,
$E_o(R-V) =  -0.47 \pm   0.03$,
$E_o(i-V) =  -0.92 \pm   0.03$
are plotted in Figure~\ref{sn2014j:fig}.
These data are fit to the model
\begin{equation}
E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)x_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)x_1,
\end{equation}
where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab} and the fit
parameters $x_i $.

@@

The best-fit parameters for SN~2014J are 
%----
$x_0= 2.65$, $ x_1=-1.64$ with covariance
%----
\begin{equation}
\begin{pmatrix}
0.048 & 0.047 \\
0.047 & 0.248
\end{pmatrix}.
\end{equation}
The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} using
UV through NIR data,
a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$, 
is also plotted.  Our model predictions provide a significantly better match to the data.
